\mytitle

### 2015-08-05 MSc_diss.tex
Updates in section about O3 and individual ANs

\begin{table} % RH and ANs
\caption{Alkyl nitrates and their parent alkanes}\label{tab:RHandANS}
\centering
\begin{tabular}{llll}
\hline
Parent alkane& Structural formula          & Name                     & Group\\
\hline
$CH_4$       & $CH_3ONO_2$                 & methyl nitrate           & $CH_3ONO_2$ \\
\hline
$C_2H_6$     & $CH_3CH_2ONO_2$             & ethyl nitrate            & $C_2H_5ONO_2$ \\
\hline
$C_3H_8$     & $(CH_3)_2CHONO_2$           & iso-propyl nitrate       & $\Sigma C_3H_7ONO_2$\\
             & $CH_3(CH_2)_2ONO_2$         & n-propyl nitrate         & \\
\hline
$nC_4H_{10}$ & $CH_3(CH_2)_3ONO_2$         & n-butyl nitrate          & $\Sigma nC_4H_9ONO_2$\\
             & $CH_3CH_2CH(CH_3)ONO_2$     & sec-butyl nitrate        & \\
\hline
$iC_4H_{10}$ & $CH_3CH(CH_3)CH_2ONO_2$     & iso-butyl nitrate        & $\Sigma iC_4H_9ONO_2$\\
             & $CH_2C(CH_3)CH_2ONO_2$      & tert-butyl nitrate       & \\
\hline
$nC_5H_{12}$ & $CH_3(CH_2)_4ONO_2$         & n-pentyl nitrate         & $\Sigma nC_5H_{11}ONO_2$\\
             & $CH_3(CH_2)_2CH(CH_3)ONO_2$ & 2-pentyl nitrate         & \\
             & $???$                       & 3-pentyl nitrate         & \\
\hline
$iC_5H_{12}$ & $???$                       & 2-methylbutyl nitrate    & $\Sigma iC_5H_{11}ONO_2$\\
             & $(CH_3)_2CH(CH_2)_2ONO_2$   & 3-methyl-2-butyl nitrate & \\
             & $(CH_3)_2C(CH_2CH_3)ONO_2$  & 2-methyl-2-butyl nitrate & \\
\hline
\end{tabular}
\end{table}

@@

To estimate the impact of individual alkyl nitrates or their groups on $O_3$ production an additional series of experiments have been conducted (Figure \ref{fig:timeO3diff10ppbNOx6VOC}).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\includegraphics[width=0.7\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/allAN/chem_allAN_timeO3diff_10ppbNOx6VOC.eps}
\caption{Time evolution of the difference in $O_3$ mixing ratio between base experiment (with all alkyl nitrate chemistry switched on) and experiments where chemistry of individual alkyl nitrates or their groups is switch on. Black line shows the difference between base experiment and an experiment with all alkyl nitrate chemistry switched off. $NO_x$ = 10 ppb, $VOCs$ = case F.}\label{fig:timeO3diff10ppbNOx6VOC}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
\caption{Difference in $O_3$ mixing ratio by the end of simulation depending alkyl nitrate chemistry.}\label{tab:timeO3diff10ppbNOx6VOC}
\begin{tabular}{cc}
\hline
Alkyl nitrate            & $O_3$ difference (ppb) \\
\hline
$CH_3ONO_2$              & -11.5 \\
$C_2H_5ONO_2$            & -11.6 \\
$\Sigma C_3H7ONO_2$      & -10.5 \\
$\Sigma nC_4H_9ONO_2$    & -8.7  \\
$\Sigma iC_4H_9ONO_2$    & -11.0 \\
$\Sigma nC_5H_{11}ONO_2$ & -10.1 \\
$\Sigma iC_5H_{11}ONO_2$ & -8.0  \\
$\Sigma RONO_2$          & -11.9 \\
\hline
\end{tabular}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\begin{table} % RH and ANs
\caption{Alkyl nitrates and their parent alkanes}\label{tab:RHandANs}
\centering
\begin{tabular}{llll}
\hline
Parent alkane& Structural formula          & Name                     & Group\\
\hline
$CH_4$       & $CH_3ONO_2$                 & methyl nitrate           & $CH_3ONO_2$ \\
\hline
$C_2H_6$     & $CH_3CH_2ONO_2$             & ethyl nitrate            & $C_2H_5ONO_2$ \\
\hline
$C_3H_8$     & $(CH_3)_2CHONO_2$           & iso-propyl nitrate       & $\Sigma C_3H_7ONO_2$\\
             & $CH_3(CH_2)_2ONO_2$         & n-propyl nitrate         & \\
\hline
$nC_4H_{10}$ & $CH_3(CH_2)_3ONO_2$         & n-butyl nitrate          & $\Sigma nC_4H_9ONO_2$\\
             & $CH_3CH_2CH(CH_3)ONO_2$     & sec-butyl nitrate        & \\
\hline
$iC_4H_{10}$ & $CH_3CH(CH_3)CH_2ONO_2$     & iso-butyl nitrate        & $\Sigma iC_4H_9ONO_2$\\
             & $CH_2C(CH_3)CH_2ONO_2$      & tert-butyl nitrate       & \\
\hline
$nC_5H_{12}$ & $CH_3(CH_2)_4ONO_2$         & n-pentyl nitrate         & $\Sigma nC_5H_{11}ONO_2$\\
             & $CH_3(CH_2)_2CH(CH_3)ONO_2$ & 2-pentyl nitrate         & \\
             & $???$                       & 3-pentyl nitrate         & \\
\hline
$iC_5H_{12}$ & $???$                       & 2-methylbutyl nitrate    & $\Sigma iC_5H_{11}ONO_2$\\
             & $(CH_3)_2CH(CH_2)_2ONO_2$   & 3-methyl-2-butyl nitrate & \\
             & $(CH_3)_2C(CH_2CH_3)ONO_2$  & 2-methyl-2-butyl nitrate & \\
\hline
\end{tabular}
\end{table}

@@

To estimate the impact of individual alkyl nitrates on $O_3$ production an additional series of experiments have been conducted. Prior to calculations some of the alkyl nitrates have been gathered into groups according to their parent alkanes as it shown in Table \ref{tab:RHandANs}. Setting initial $NO_x$ mixing ratio to 10 ppb and taking the middlemost $VOCs$ initial values (i.e., case F), the model has been run with certain alkyl nitrate chemistry switched on. For example, to estimate the impact of $CH_3ONO_2$ the reactions involving this nitrate were switched on, while the other reactions with nitrates were switched off. Experiment with all alkyl nitrate chemistry is considered as a base run.

To estimate the impact of certain alkyl nitrates on $O_3$ the difference between base run and other runs including one with all alkyl nitrate chemistry switched off has been calculated. Figure \ref{fig:timeO3diff10ppbNOx6VOC} shows the time evolution of this difference. This difference becomes more and more negative with time as the mixing ratio of alkyl nitrates themselves rises (Figure \ref{fig:timeANs10ppbNOx6VOC}). By the end of simulation the drop in $O_3$ mixing ratio due to the rise in mixing ratio of total alkyl nitrates is equal to -11.9 ppb (Table \ref{tab:timeO3diffANs10ppbNOx6VOC}.

The contribution of different alkyl nitrates to drop in $O_3$ is not the same. By the end of simulation, the drop in $O_3$ mixing ratio due to ethyl nitrate only ($C_2H_5ONO_2$) is 11.6 ppb, and is almost the same drop is caused by methyl nitrate.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\includegraphics[width=0.7\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/allAN/chem_allAN_timeO3diff_10ppbNOx6VOC.eps}
\caption{Time evolution of the difference in $O_3$ mixing ratio between base experiment (with all alkyl nitrate chemistry switched on) and experiments where chemistry of individual alkyl nitrates or their groups is switch on. Black line shows the difference between base experiment and an experiment with all alkyl nitrate chemistry switched off. $NO_x$ = 10 ppb, $VOCs$ = case F.}\label{fig:timeO3diff10ppbNOx6VOC}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\includegraphics[width=0.7\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/allAN/chem_allAN_timeANs_10ppbNOx6VOC.eps}
\caption{Time evolution of alkyl nitrates mixing ratios. $NO_x$ = 10 ppb, $VOCs$ = case F.}\label{fig:timeANs10ppbNOx6VOC}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
\caption{Difference in $O_3$ mixing ratio by the end of simulation depending alkyl nitrate chemistry.}\label{tab:timeO3diffANs10ppbNOx6VOC}
\begin{tabular}{ccc}
\hline
Alkyl nitrate            & $RONO_2$ mixing ratio (ppt) & $O_3$ difference (ppb) \\
\hline
$CH_3ONO_2$              & 43  & -11.5 \\
$C_2H_5ONO_2$            & 38  & -11.6 \\
$\Sigma C_3H7ONO_2$      & 115 & -10.5 \\
$\Sigma nC_4H_9ONO_2$    & 192 & -8.7  \\
$\Sigma iC_4H_9ONO_2$    & 81  & -11.0 \\
$\Sigma nC_5H_{11}ONO_2$ & 108 & -10.1 \\
$\Sigma iC_5H_{11}ONO_2$ & 290 & -8.0  \\
$\Sigma RONO_2$          & 867 & -11.9 \\
\hline
\end{tabular}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
